\documentclass{article}
\usepackage[utf8]{inputenc}

\title{BlueMix is Now IBM Cloud}
\author{brucwalk }
\date{February 2018}

%\usepackage
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex} %Imports biblatex package
\addbibresource{hid-sp18-525.bib} %Import the bibliography file

\begin{document}
In 2017, IBM fully committed to cloud computing.  IBM BlueMix is now IBM Cloud.  The changes go far beyond the name.  The new platform gives IBM a new, singular way to engage customers.  \cite{hid-sp18-525-bluemix} Now, services are available on public or private clouds, with added capabilities, including database, artificial intelligence, and blockchain. \cite{hid-sp18-525-bluemix}

In IBM Cloud, many popular services and applications are available, with public or private access No cloud presence is possible without a strong network.  IBM has included an industry leading level of network capabilities.  To ensure security, access, and redundancy, IBM operates 60 data centers. \cite{hid-sp18-525-bluemix}  

The IBM Cloud connects data science and other tools, such as VMware, SAP, Spark, Jupyter, R, and many others. \cite{hid-sp18-525-bluemix} Both open source and proprietary applications and services are part of IBM Cloud.

As an industry leader in blockchain, IBM’s use of the technology is featured in IBM Cloud.  Blockchain is becoming the most known product IBM offers, and it is a major componet of IBM Cloud. \cite{hid-sp18-525-bluemix} 


\maketitle

\section{Introduction}

\end{document}
